Delayed effects of climate on vital rates leads to demographic divergence in Amazonian forest fragments

### 2021-06-14 doc/paper.Rmd
add placeholders for additional required sections

---
title: "Delayed effects of climate on vital rates leads to demographic divergence in Amazonian forest fragments"
author:
  - Eric R. Scott:
      email: scottericr@gmail.com
      institute: [UF_WEC]
      correspondence: true
  - María Uriarte:
      email: mu2126@columbia.edu
      institute: [Columbia]
      correspondence: false
  - Emilio M. Bruna:
      email: embruna@ufl.edu
      institute: [UF_WEC, UF_LAS, BDFFP]
      correspondence: false

@@

>>>>

---
title: "Delayed effects of climate on vital rates leads to demographic divergence in Amazonian forest fragments"
shorttitle: "Delayed effects of climate on vital rates"
author:
  - Eric R. Scott:
      email: scottericr@gmail.com
      institute: [UF_WEC]
      correspondence: true
  - María Uriarte:
      email: mu2126@columbia.edu
      institute: [Columbia]
      correspondence: false
  - Emilio M. Bruna:
      email: embruna@ufl.edu
      institute: [UF_WEC, UF_LAS, BDFFP]
      correspondence: false

@@

# Data Availability Statement

All data and code used in this study are available at [insert zenodo link].
